\section*{Standard Model Physics}
The Standard Model of particle physics refers to the current, most accurate model of fundamental particles and their respective interactions. 
This is a model is constructed from gauge theories of quarks and leptons \cite{Kuno:1999jp}. 
This proposes three fundamental forces: electromagnetic, strong and weak. 
The interactions and behaviour of fundamental particles is governed by these three forces. 
As well as the interactions and behaviour, the standard model also describes the fundamental particles and their associated properties. 
Under the standard model, the fundamental particles can be categorised into six quarks and six leptons, further subdivided into three generations.
\section*{Leptons}
Leptons are spin half particles like quarks, Also like quarks, leptons are separated into three different flavours. 
These three flavours have a respective lepton number, this is a quantum number associated with the particle of that flavour. 
Three flavours of leptons have been observed, electronic, muonic and tauonic. 
The numbers are assigned as such: $L = e, \mu, \tau \text{and} \nu_{e, \mu, \tau}$ have a lepton number of $+1$ and $\bar{L} = \bar{e}, \bar{\mu}, \bar{\tau} \text{and} \bar{\nu}_{e, \mu, \tau}$ have a lepton number of $-1$. 
The Standard Model Lagrangian is invariant, that being it has a symmetry associated with each lepton generation. 
Fermion masses and mixing between generations comes from the Yukawa couplings of fermion fields with the Higgs field. 
For leptons the lagrangian for this coupling is invariant under three distinct, global U(1) symmetries \cite{Calibbi}. 
These three symmetries represent the three distinct lepton generations. 
The result of this is that lepton number is a conserved quantity under the current Standard Model. 
This is under the condition that no interaction leads to neutrinos with non-zero masses.
\section*{Lepton Flavour Violation}
The standard model in it's most basic form describes lepton number as a conserved quantity under the condition that neutrinos are left-handed, massless particles. 
This idea has since been shown to be incorrect with experiments revealing both a neutrino mass and lepton number violation through neutrino oscillations.
\section*{Mu3e Physics}
The Mu3e experiment 